### 2017-07-19 profiles_examples.Rmd
Re-export the pipe function for outside use (not just within the package development)

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(tidyverse)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% sample_n(size = 500) %>% 
  mutate(frisco = case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  select(age, sex, frisco, drugs, height, status)
```

>>>>

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(frisco = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, frisco, drugs, height, status)
```
